6.867 Problem Set 1

### 2015-10-02 pset1/paper.tex
asdf

We repeated our experiment from section 3 in this section, fitting weight vectors for values of $M$ between 0 and 9 (inclusive), and values of $\lambda$ of the form $2^{k/2}$ for integers $-3 \le k \le 11$. We found the cross-validation error for each weight vector, and discovered that $(M, \lambda) = (2, 2^{-3})$ resulted in the lowest cross-validation error, while $(M, \lambda) = (6, 2^{-1})$ resulted in the highest. However, the best and worst CV errors differed by only one order of magnitude, which surprised us. We believe this is due to an affinity towards median behavior of this method, as the value with the least absolute error with respect to a set of values is the median of that set. The best and worst fits are depicted in Figure \ref{p4figure}.

>>>>

We repeated our experiment from section 3 in this section, fitting weight vectors for values of $M$ between 0 and 9 (inclusive), and values of $\lambda$ of the form $2^{k/2}$ for integers $-6 \le k \le 11$. We found the cross-validation error for each weight vector, and discovered that $(M, \lambda) = (2, 2^{-3})$ resulted in the lowest cross-validation error, while $(M, \lambda) = (6, 2^{-1})$ resulted in the highest. However, the best and worst CV errors differed by only one order of magnitude, which surprised us. We believe this is due to an affinity towards median behavior of this method, as the value with the least absolute error with respect to a set of values is the median of that set. The best and worst fits are depicted in Figure \ref{p4figure}.
